Ethnographic Study of Online Entertainers

### 2017-03-17 proposals/Brown_Magic_Grant_2017/main.tex
oh right forgot to state the obvious
updates to framing based on conversation with msb and some of ethan's feedback also added some bullet points to the research plan

% \section*{Insight}
\topic{Studying contemporary phenomena through an established framing
can be a helpful way of
making sense of what we've seen so far, as well as
providing us with some grounding to make predictions.}
We've done this before, studying crowd work and gig work as
a modern instantiation of \textit{piecework}~\cite{pieceworkCrowdworkGigwork}.
This positioning of an existing subject in historical context not only
provided us with guidance toward some of the major threads of research
in crowdsourcing, but
also informed some of the potential futures of crowdsourcing and
the ever growing gig work labor markets.

\topic{We can liken some aspects of online performance art on YouTube and Twitch
to street performance and busking,
allowing us to relate ostensibly new phenomena to robust scholarship.}
As is the case with street performance,
online performance isn't restricted to classically trained professionals;
instead, performers (both online and in the streets) practice more experimental 
drawing on their candid interaction with their audiences,
which can change from one performance to the next.

\topic{This connection has purchase, but it has flaws, mostly owing to the unique nature of ``networked publics''~\cite{boyd2007youth}.}
For one thing, most video sharing websites keep videos
% --- the modern performances ---
in perpetuity
--- that is, unless a complaint over copyright infringement is filed, in which case the lifespan of that ``performance'' can be cut short.
The public that congregates around a performer, too, has similar permanence that offline busking doesn't;
YouTube comments linger for years after they're made.

@@

\section*{Research Proposal}

\section*{Broader Impact}
\topic{Formally recognized art forms have assimilated emergent genres and types of performance art in the past, and
we should expect that they will continue to do so.}
Jazz was born out of what largely ``\dots was recognized~\dots~as being but one species of the genus, ragtime played by ear by fakers\dots''~\cite{10.2307/779456}.
Even further back in history, \nth{17} century street performance in Japan blended ``\dots every imaginable genus and species of popular song and dance\dots'' and
kabuki, in its early years,
``would hardly have been recognized or condoned [by traditional performers]''~\cite{groemer2016street}.

\ali{something like: if this continues, then we should infer that
     the future of this type of performance art will bear heavily on
     the direction and trajectory of digitally mediated entertainment and performance}

\section*{Demonstrate viability}

\section*{Expected outcomes}

>>>>

\topic{One issue frustrating this potential research area is that
the platforms have changed so dramatically in as few as 5 to 10 years that
it can seem as though researchers are trying to wade through shifting sands.}
Scholarship on content creators loses bearing rapidly when economic factors motivate aspiring professional entertainers to join the community~\cite{Hamilton:2014:STF:2611105.2557048};
the tension between these entertainers experimenting with content remixing and
the holders of the copyright of the source material
(for example, see~\cite{Hilderbrand48})
shifts dramatically when
the platform's copyright enforcement mechanisms advance
not just incrementally but substantially~\cite{kim2012institutionalization}.

% \section*{Insight}
\topic{We recognize that \textit{historical analysis}
% Studying contemporary phenomena through an established framing
can be a helpful way of
making sense of contemporary phenomena.}
As we found in a recent paper framing crowd work and gig work as a modern instantiation of \textit{piecework},
scholarship from a parallel or similar domain can
provide us some grounding to make sense of what we've seen, as well as inform predictions~\cite{pieceworkCrowdworkGigwork}.
% This positioning of an existing subject in historical context not only
% provided us with guidance toward some of the major threads of research
% in crowdsourcing, but
% also informed some of the potential futures of crowdsourcing and
% the ever growing gig work labor markets.

\topic{To that end, we can liken some aspects of online performance art on YouTube and Twitch
to street performance and busking,
allowing us to relate ostensibly new phenomena to robust scholarship.}
As is the case with street performance,
online performance isn't restricted to classically trained professionals;
instead, performers (both online and in the streets) practice more experimental 
drawing on their candid interaction with their audiences,
which can change from one performance to the next.

\topic{This connection has purchase, but it has flaws, mostly owing to the unique nature of ``networked publics''~\cite{boyd2007youth}.}
For one thing, most video sharing websites keep videos
% --- the modern performances ---
in perpetuity
--- that is, unless a complaint over copyright infringement is filed, in which case the lifespan of that ``performance'' can be cut short.
The public that congregates around a performer, too, has similar permanence that offline busking doesn't;
YouTube comments linger for years after they're made.
And these say nothing of the different nature of algorithmic enforcement of rules and policies, and
the near--perfect ability of these platforms to redirect revenue and even people's focus instantaneously.

@@

\section*{Research Plan}
\ali{Basic plan:
\begin{itemize}
  \item contact YouTube channels that have more than 1M subscribers
        (and have mentioned YouTube policies at some point
          (suggesting maybe passing interest in discussing meta topics)?)
  \item Reach out by any contact methods they provide (if none, then skip)
  \item Semi--structured interview guiding towards:
  \begin{itemize}
    \item interaction with platform \& its designers
    \item engagement with audience
    \item coordination with other YouTubers (if any)
  \end{itemize}
  \item tentative questions include:
  \begin{itemize}
    \item platform questions
    \begin{enumerate}
      \item when did you switch to (streaming/YouTubing) as primary career?
      \item what's YouTube's relationship with you?
      \item if you were telling a new YouTuber how to get started,
            what would you say they should know about YouTube
            (the system, the company, etc\dots)
            that's not immediately obvious?
    \end{enumerate}
    \item audience questions
    \begin{enumerate}
      \item how do you interact with audiences?
      \item what sorts of comments do you get?
      \item do you reply?
      \item do you change your future content based on feedback in the comments?
    \end{enumerate}
    \item peer questions
    \begin{enumerate}
      \item what's your sense of the community as a whole?
      \item how many other YouTubers do you know
            (let's say you've had a chat with them in the last month and
             will probably do so again in the next month)?
      \item are you all cooperative? competitive? what's the culture like?
    \end{enumerate}
  \end{itemize}
\end{itemize}
}

% \section*{Broader Impact}
% \topic{Formally recognized art forms have assimilated emergent genres and types of performance art in the past, and
% we should expect that they will continue to do so.}
% Jazz was born out of what largely ``\dots was recognized~\dots~as being but one species of the genus, ragtime played by ear by fakers\dots''~\cite{10.2307/779456}.
% Even further back in history, \nth{17} century street performance in Japan blended ``\dots every imaginable genus and species of popular song and dance\dots'' and
% kabuki, in its early years,
% ``would hardly have been recognized or condoned [by traditional performers]''~\cite{groemer2016street}.

% \ali{something like: if this continues, then we should infer that
%      the future of this type of performance art will bear heavily on
%      the direction and trajectory of digitally mediated entertainment and performance}

% \section*{Demonstrate viability}

% \section*{Expected outcomes}
